---
title: "Monte Carlo analysis of Bitcoin"
author: "Lukas Läderach"
output: html_notebook
---
# Abstract
This document describes the process of modeling a bitcoin monte carlo chart.

# Prerequisites
To follow along this notebook make sure you have the following R-Packages installed globally.

```{r}
# Get millions of financial and economic datasets from hundreds of publishers directly into R.
install.packages("Quandl")
# ggplot2 is a plotting system for R, based on the grammar of graphics.
install.packages("ggplot2")
```

Once those packages are installed import them into your current workspace and set your Quandl API-Key (You have to create an account at [Quandl](https://www.quandl.com/sign-up-modal?defaultModal=showSignUp)).

```{r}
library(Quandl)
library(ggplot2)

Quandl.api_key("CYyznmeKqzV2GxrHZMxD")
```

Once everthing is set up correctly you should be able retrieve financial data via Quandl.

For example the following statement will retrieve all the BTC/USD starting from 2017-12-31 to the very recent.

```{r}
data <- Quandl("BITFINEX/BTCUSD", start_date="2017-12-31")
head(data)
```

To generate a plot visualizing the closing price according to it's date (column labeled *Last*) we can specify which columns to retrieve via the column_index parameter (0 is always the *Date* column). To specifiy multiple columns we can also create a vector e.g. *c(4,6)* - this would return a table containing the *Date*, *Last* and *Ask* columns only.

```{r}
data <- Quandl("BITFINEX/BTCUSD", start_date="2011-12-31", column_index=4)
qplot(Date, Last, data=data, geom="line")
```


# Introduction

# Methods

# Results


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
head(Quandl("BITFINEX/BTCUSD", start_date="2017-12-31"), column_index=4)
